SubsidyExplorer - Step 10: Final database of all pre-populated reform proposals

### 2022-09-20 scripts/10_final_proposal_database.Rmd
final database

title: "SubsidyExplorer - Step 7: Pre-Populated Proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

@@

# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.5
end_year <- 2080
folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_FINAL_AGREEMENT/")

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), folder_name)
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))

@@

vessel_dat <- vessel_dat %>%
   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
  ungroup() %>%
  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
         good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))

@@

```{r}
# Proposal settings
#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
#   dplyr::filter(include != "Hide")
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>%
  dplyr::filter(include != "Hide")

# Proposal names
included_proposals <- proposal_settings %>%
  dplyr::filter(include %in% c("Yes", "Alternate")) %>%
  mutate(display_name = case_when(proposal == "Default" ~ "None",
                                  TRUE ~ title_tool)) %>%
  dplyr::select(category, proposal, display_name) %>%
  arrange(category) %>%
  dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) # remove blank entries for tool

@@

```{r}
# 1) Cap/tier lookup table
cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv"))

# S&DT lookup table
sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv"))

## Model proposals

```{r}
proposal_results <- NULL

for(i in 2:length(proposal_choices)){

@@

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies,
      sdt_lookup = sdt_lookup_table)

    # Make list
    fleet_list <- fleet$summary %>%
      group_by(region) %>%
      group_split()
    names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)]

@@

    # Extract results timeseries
    results_all <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name),
             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))

      write_csv(results_all, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))

    # Add to data frame
      proposal_results <- proposal_results %>%
        bind_rows(results_all)

@@

Make plots with all proposals and the most ambitious result

@@

plot_results <- proposal_results %>%
  bind_rows(most_ambitious_results)

# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                           spatial_res = "global",
                                           temporal_res = "all",
                                           start_year = 2018,
                                           end_year = end_year,
                                           plot_name = "all_proposals_ts_plot",
                                           plot_width = 8,
                                           plot_height = 10,
                                           results_dir = results_dir,
                                           group_var = "run_id",
                                           color_var = "run_group",
                                           legend_pos_manual = "bottom",
                                           legend_name = "Scenario Type")

  # 2) global (aggregated) "kobe" final year plot
  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = end_year,
                                            plot_name = "all_proposals_end_plot",
                                            plot_width = 8,
                                            plot_height = 6,
                                            results_dir = results_dir,
                                            group_var = "run_id",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type")

  # 2) global (aggregated) "kobe" final year plot
  compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2050,
                                            plot_name = "all_proposals_2050_plot",
                                            plot_width = 7.5,
                                            plot_height = 4,
                                            results_dir = results_dir,
                                            group_var = "run_id",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type")

  # 3) regional timeseries plot
  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                                    spatial_res = "regional",
                                                    temporal_res = "all",
                                                    start_year = 2018,
                                                    end_year = end_year,
                                                    plot_name = "regional_all_proposals_ts_plot",
                                                    plot_width = 12,
                                                    plot_height = 10,
                                                    results_dir = results_dir,
                                                    group_var = "run_id",
                                                    color_var = "run_group",
                                                    legend_pos_manual = "bottom",
                                                    legend_name = "Scenario Type")

  # 4) regional "kobe" final year plot
  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                                     spatial_res = "regional",
                                                     temporal_res = "last",
                                                     end_year = end_year,
                                                     plot_name = "regional_all_proposals_end_plot",
                                                     plot_width = 12,
                                                     plot_height = 8,
                                                     results_dir = results_dir,
                                                     group_var = "run_id",
                                                     color_var = "run_group",
                                                     legend_pos_manual = "bottom",
                                                     legend_name = "Scenario Type")

  # 4) regional "kobe" final year plot
  regional_compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
                                                     spatial_res = "regional",
                                                     temporal_res = "last",
                                                     end_year = 2050,
                                                     plot_name = "regional_all_proposals_2050_plot",
                                                     plot_width = 12,
                                                     plot_height = 8,
                                                     results_dir = results_dir,
                                                     group_var = "run_id",
                                                     color_var = "run_group",
                                                     legend_pos_manual = "bottom",
                                                     legend_name = "Scenario Type")
}
```

```{r}
if(make_plots){
  # A) global (aggregated) "kobe" final year plot
  box_2050_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = 2050,
                                            plot_name = "box_scenario_type_2050_plot",
                                            plot_width = 7.5,
                                            plot_height = 6,
                                            results_dir = results_dir,
                                            group_var = "run_group",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type",
                                            plot_type = "box")

figure_5 <- cowplot::plot_grid(box_2050_plot, compare_2050_plot, ncol = 1, rel_heights = c(1,0.75), axis = "lr", align = "v", labels = c("(A)", "(B)"), hjust = -1)
ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)
}
```
## Extract 2050 and end year results for all proposals and save as nice tables

@@

# Collect global results
all_results_global_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_global_output_table_2050_pretty <- all_results_global_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))

@@

# Now make a min, max, and average for each proposal type
summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
  group_by(Category, Year, Variable) %>%
  summarize(Minimum = min(Value, na.rm = T),
            Maximum = max(Value, na.rm = T),
            Median = median(Value, na.rm = T),
            Mean = mean(Value, na.rm = T)) %>%
  arrange(Category)

write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))

# Get rounded end values for the most ambitious scenario
global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
```

```{r}
# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Region, Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))

@@

# Now make a min, max, and average for each proposal type
summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
  group_by(Region, Category, Year, Variable) %>%
  summarize(Minimum = min(Value, na.rm = T),
            Maximum = max(Value, na.rm = T),
            Median = median(Value, na.rm = T),
            Mean = mean(Value, na.rm = T)) %>%
  arrange(Region, Category)

write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
```

@@

```{r}
# # We want these to be ordered by date within each category, so we need to go back to our list
# date_order <- proposal_settings %>%
#   dplyr::select(title_tool, date) %>%
#   rownames_to_column("order") %>%
#   mutate(order = as.numeric(order))

>>>>

title: "SubsidyExplorer - Step 10: Final database of all pre-populated reform proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

@@

This script generates databases of results (global and regional) for all pre-populated proposals contained within the SubsidyExplorer tool. This includes the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

@@

# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.5
end_year <- 2080
folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_ALL/")

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "10-final-database/"), folder_name)
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Load vessel list
vessel_dat_raw <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))

@@

vessel_dat <- vessel_dat_raw %>%
   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
  ungroup() %>%
  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
         good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))

@@

```{r}
# Load proposal settings
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>%
  dplyr::filter(include != "Hide")

# Filter to final list of proposals to be included in database
included_proposals <- proposal_settings %>%
  dplyr::filter(include %in% c("Yes", "Alternate")) %>%
  mutate(display_name = case_when(proposal == "Default" ~ "None",
                                  TRUE ~ title_tool)) %>%
  dplyr::select(category, proposal, display_name) %>%
  arrange(category) %>%
  dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) %>% # remove blank entries created for tool
  dplyr::filter(proposal != "Default")

@@

```{r}
# Load cap/tier lookup table
cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv"))

# Load S&DT lookup table
sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv"))
```
## Model proposals

```{r}
proposal_results <- NULL
affected_subs <- NULL

for(i in 1:length(proposal_choices)){

@@

   # Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies,
      sdt_lookup = sdt_lookup_table)

    # Make list of fleets for bioeconomic model
    fleet_list <- fleet$summary %>%
      group_by(region) %>%
      group_split()
    names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)]

@@

    # Extract model timeseries results
    results_ts <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name),
             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))

      write_csv(results_ts, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))

    # Add to data frame
      proposal_results <- proposal_results %>%
        bind_rows(results_ts)

    # Extract affected/unaffected subsidies amounts and convert back to absolute dollars
      affected_subs_raw <- fleet$vessels %>%
        group_by(region) %>%
        summarize_at(vars(A1_subs:C3_subs, A1_subs_removed:C3_subs_removed), sum, na.rm = T) %>%
        gather("type", "value", -region) %>%
        mutate(category = ifelse(grepl("removed", type), "removed", "base")) %>%
        mutate(type = str_replace(type, "_subs_removed", "")) %>%
        mutate(type = str_replace(type, "_subs", "")) %>%
        left_join(rel, by = "type") %>%
        mutate(rel_effect_effort = ifelse(is.na(rel_effect_effort), 1, rel_effect_effort)) %>%
        mutate(value_real = value/rel_effect_effort) %>%
        group_by(region, category) %>%
        summarize(value_real = sum(value_real, na.rm = T)) %>%
        ungroup() %>%
        group_by(region) %>%
        summarize(subs_base = value_real[category == "base"],
                  subs_affected = value_real[category == "removed"],
                  percent_subs_affected = (value_real[category == "removed"]/value_real[category == "base"])*100)

      affected_subs_out <- data_frame(run_id = rep(proposal_name, length.out = 3),
                                      run_name = rep(names(proposal_name), length.out = 3),
                                      run_group = rep(unique(proposal_settings$category[proposal_settings$proposal == proposal_name]), length.out = 3),
                                      region = c("atlantic", "indian", "pacific")) %>%
        left_join(affected_subs_raw, by = "region")

      # Add to data frame
      affected_subs <- affected_subs %>%
        bind_rows(affected_subs_out)

@@

Add in most ambitious result and combine into single dataset

@@

# Combine with ts data
all_ts_results <- proposal_results %>%
  bind_rows(most_ambitious_results)

# Get subsidies affected for most ambitious scenario
most_ambitious_subs_affected <- vessel_dat_raw %>%
  mutate(subs_base = bad_subs + good_subs + ugly_subs,
         subs_affected = bad_subs + ugly_subs) %>%
  group_by(region) %>%
  summarize(subs_base = sum(subs_base, na.rm = T),
            subs_affected = sum(subs_affected, na.rm = T)) %>%
  mutate(percent_subs_affected = (subs_affected/subs_base)*100)

# Combine with subs affected data
all_subs_affected <- data_frame(run_id = rep("Ambitious Reform", 3),
                                run_name = rep("All bad and ugly subsidies", 3),
                                run_group = rep("Ambitious Reform", 3)) %>%
  bind_cols(most_ambitious_subs_affected) %>%
  bind_rows(affected_subs)
```

## Make nice databases (global and regional)

@@

# Collect global results
all_results_global_output_table <- all_ts_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_global_output_table_2050_pretty <- all_results_global_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
  rename(`Change in biomass (%, 2050)` = Biomass,
         `Change in catch (%, 2050)` = Catches,
         `Change in revenue (%, 2050)` = Revenue,
         `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>%
  dplyr::select(-Year)

@@

# Now make a pretty version for 2080 only
all_results_global_output_table_2080_pretty <- all_results_global_output_table %>%
  dplyr::filter(Year == 2080) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
  rename(`Change in biomass (%, 2080)` = Biomass,
         `Change in catch (%, 2080)` = Catches,
         `Change in revenue (%, 2080)` = Revenue,
         `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>%
  dplyr::select(-Year)

write.csv(all_results_global_output_table_2080_pretty, paste0(results_dir, "all_results_global_output_table_2080_pretty.csv"))

# Combine
all_results_global_output_table_pretty <- all_results_global_output_table_2050_pretty %>%
  left_join(all_results_global_output_table_2080_pretty %>% dplyr::select(-Name, -Category))

write.csv(all_results_global_output_table_pretty, paste0(results_dir, "all_results_global_output_table_pretty.csv"))

# Now let's get affected subs globally
all_subs_affected_global <- all_subs_affected %>%
  group_by(run_id, run_name, run_group) %>%
  summarize(subs_base = sum(subs_base),
            subs_affected = sum(subs_affected)) %>%
  ungroup() %>%
  mutate(percent_subs_affected = round((subs_affected/subs_base)*100, 2))

# And add to table
global_database <- all_results_global_output_table_pretty %>%
  left_join(all_subs_affected_global %>% dplyr::select(Id = run_id, subs_affected, percent_subs_affected)) %>%
  rename(`Subsidies affected ($)` = subs_affected,
         `Subsidies affected (%)` = percent_subs_affected)

write.csv(global_database, paste0(results_dir, "SubsidyExplorer_proposal_results_global.csv"))
```

```{r}
# Now do regional
all_results_regional_output_table <- all_ts_results %>%
  dplyr::filter(Year %in% c(2050, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff) %>%
  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
  arrange(Region, Category, order, Year) %>%
  dplyr::select(-order)

@@

# Now make a pretty version for 2050 only
all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>%
  dplyr::filter(Year == 2050) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
  rename(`Change in biomass (%, 2050)` = Biomass,
         `Change in catch (%, 2050)` = Catches,
         `Change in revenue (%, 2050)` = Revenue,
         `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>%
  dplyr::select(-Year) %>%
  mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
                            Region == "indian" ~ "Indian Ocean",
                            Region == "pacific" ~ "Pacific Ocean"))

@@

# Now make a pretty version for 2080 only
all_results_regional_output_table_2080_pretty <- all_results_regional_output_table %>%
  dplyr::filter(Year == 2080) %>%
  ungroup() %>%
  mutate(Biomass = round(Biomass*100, 2),
         Catches = round(Catches*100, 2),
         Revenue = round(Revenue*100, 2),
         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
  rename(`Change in biomass (%, 2080)` = Biomass,
         `Change in catch (%, 2080)` = Catches,
         `Change in revenue (%, 2080)` = Revenue,
         `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>%
  dplyr::select(-Year) %>%
  mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
                            Region == "indian" ~ "Indian Ocean",
                            Region == "pacific" ~ "Pacific Ocean"))

write.csv(all_results_regional_output_table_2080_pretty, paste0(results_dir, "all_results_regional_output_table_2080_pretty.csv"))

# Combine
all_results_regional_output_table_pretty <- all_results_regional_output_table_2050_pretty %>%
  left_join(all_results_regional_output_table_2080_pretty %>% dplyr::select(-Name, -Category))

write.csv(all_results_regional_output_table_pretty, paste0(results_dir, "all_results_regional_output_table_pretty.csv"))

# And add affected subsidies to table
regional_database <- all_results_regional_output_table_pretty %>%
  left_join(all_subs_affected %>%
              mutate(region = case_when(region == "atlantic" ~ "Atlantic Ocean",
                                        region == "indian" ~ "Indian Ocean",
                                        region == "pacific" ~ "Pacific Ocean")) %>%
              mutate(percent_subs_affected = round(percent_subs_affected, 2)) %>%
              dplyr::select(Id = run_id, Region = region, subs_affected, percent_subs_affected)) %>%
  rename(`Subsidies affected ($)` = subs_affected,
         `Subsidies affected (%)` = percent_subs_affected)

write.csv(regional_database, paste0(results_dir, "SubsidyExplorer_proposal_results_regional.csv"))
```

```{r}
# # Now make a min, max, and average for each proposal type
# summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
#   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
#   group_by(Category, Year, Variable) %>%
#   summarize(Minimum = min(Value, na.rm = T),
#             Maximum = max(Value, na.rm = T),
#             Median = median(Value, na.rm = T),
#             Mean = mean(Value, na.rm = T)) %>%
#   arrange(Category)
# 
# write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))
# 
# # Get rounded end values for the most ambitious scenario
# global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# 
# global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
# global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

# # Now make a min, max, and average for each proposal type
# summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
#   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
#   group_by(Region, Category, Year, Variable) %>%
#   summarize(Minimum = min(Value, na.rm = T),
#             Maximum = max(Value, na.rm = T),
#             Median = median(Value, na.rm = T),
#             Mean = mean(Value, na.rm = T)) %>%
#   arrange(Region, Category)
# 
# write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
```

## Plots

```{r}
if(make_plots){
  # A) global (aggregated) "kobe" final year plot
  box_2050_plot <- BioEconomicModelPlots(dat = all_ts_results,
                                         spatial_res = "global",
                                         temporal_res = "last",
                                         end_year = 2050,
                                         plot_name = "box_scenario_type_2050_plot",
                                         plot_width = 7.5,
                                         plot_height = 6,
                                         results_dir = results_dir,
                                         group_var = "run_group",
                                         color_var = "run_group",
                                         legend_pos_manual = "bottom",
                                         legend_name = "Scenario Type",
                                         plot_type = "box")

ggsave(paste0(results_dir, "proposal_effects_2050_boxplot.tiff"), box_2050_plot, width = 7.5, height = 6)
}
```

@@

```{r}
# # We want these to be ordered by date within each category, so we need to go back to our list
# date_order <- proposal_settings %>%
#   dplyr::select(title_tool, date) %>%
#   rownames_to_column("order") %>%
#   mutate(order = as.numeric(order))
# 
# # Collect global results
# all_results_global_output_table_absolute <- plot_results %>%
#   dplyr::filter(Year %in% c(2050, end_year)) %>%
#   dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#   summarize(BAU_tot = sum(BAU, na.rm = T),
#             Reform_tot = sum(Reform, na.rm = T),
#             Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot,
#                             TRUE ~ 0)) %>%
#   ungroup() %>%
#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#                                 Variable == "catches_total" ~ "Catches",
#                                 Variable == "revenue_total" ~ "Revenue")) %>%
#   dplyr::select(Id = run_id,
#                 Name = run_name,
#                 Category = run_group, 
#                 Year,
#                 Diff_tot_absolute = Diff_tot,
#                 Variable) %>%
#   spread(Variable, Diff_tot_absolute) %>%
#   left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
#   mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
#   arrange(Category, order, Year) %>%
#   dplyr::select(-order)
# 
# write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv"))
